---
title: "How to use parallelization"
author: "G. Cornu - Forêts et Sociétés - Cirad"
date: "24/03/2021"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

Parallelization was already available using `parallel` package (through `mclApply` function) 
but was not very easy to configure. 

Now **SCGLR** is using the more modern `future` package and
it's companion package `future.apply` for apply-like functions (both are needed but 
the later will be handled internally).

See https://github.com/HenrikBengtsson/future for more information.

It will be easier to switch from simple parallelization to more complex architecture.

Parallelization is available for `scglrCrossVal` and `scglrThemeBackward` functions
(more may be added later).

## Activate parallelization

```{r eval=FALSE}
library(future)
library(future.apply) # line not needed but package must be installed

# launch a local cluster backed by R sessions
plan(multisession)

...

```

## Full code built on `scglrCrossVal` example

Nothing changes except the insertion of the code above.

```{r eval=FALSE}
library(SCGLR)
library(future)
library(future.apply) # line not needed but package must be installed

# launch a local cluster backed by R sessions
plan(multisession)

# load sample data
data(genus)

# get variable names from dataset
n <- names(genus)
ny <- n[grep("^gen",n)]    # Y <- names that begins with "gen"
nx <- n[-grep("^gen",n)]   # X <- remaining names

# remove "geology" and "surface" from nx
# as surface is offset and we want to use geology as additional covariate
nx <-nx[!nx%in%c("geology","surface")]

# build multivariate formula
# we also add "lat*lon" as computed covariate
form <- multivariateFormula(ny,c(nx,"I(lat*lon)"),A=c("geology"))

# define family
fam <- rep("poisson",length(ny))

# cross validation
genus.cv <- scglrCrossVal(formula=form, data=genus, family=fam, K=5,
  offset=genus$surface)
```

