---
title: "How display progression"
author: "G. Cornu - Forêts et Sociétés - Cirad"
date: "24/03/2021"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

Progression display is now available using `progressr` package 
(see https://github.com/HenrikBengtsson/progressr for more information).

Progression has been added to `scglrCrossVal` and `scglrThemeBackward` functions
(more can be added later).

## Activate progression

Just surround function call with `with_progress` function.

see https://github.com/HenrikBengtsson/progressr#customizing-how-progress-is-reported 
to customize progress format.

```{r eval=FALSE}
library(progressr)

# surround function call with with_progress
cv <- with_progress( scglrCrossVal(...) )

```

If you are using `R>=4.0.0` it's even simpler. You just have to activate it globally 
(no need to use `with_progress` function) and call `SCGLR` functions as usual.

```{r eval=FALSE}
progressr::handlers(global=TRUE)

...
cv <- scglrCrossVal(...)
...
```

